### 2023-11-02 main.tex
to fix

		f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(L+2-\sum_{a=1}^{m}c_{a})}{\Gamma(L+2)}

@@

It seems to me that it is more complicated than \eqref{exactCorrelations}...

>>>>

		f(L,c_{1},\ldots,c_{m})=\frac{\Gamma(2+L-\sum_{a=1}^{m}c_{a})}{\Gamma(2+L)}

@@

EQUATION TO CHECK...It seems to me that it is more complicated than \eqref{exactCorrelations}...\\
\underline{Explanation of the notation issue}:  Assume that we aim to find the 1-point correlation for $s$ at site $y$. If we compute it starting from \eqref{ABS_1} we have that all the $c_{x}$ with $x\neq y$ just disappear and we obtain 
	\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{y}=s\}}\right]=\sum_{c_{y}=0}^{1}\frac{\Gamma(2+L-c_{y})}{\Gamma(2+L)}\lambda_{s}^{c_{y}}\beta_{s}^{c_{y}}\left(2+L-y-c_{y}\right)^{c_{y}}
We do not have to keep the product over all $x$ and only the "correlated coordinate" $y$ does appear. On the other hand, if we compute 1-point correlation for $s$ at site $y$ using \eqref{ABS} we obtain 
\mathbb{E}_{\mu^{NESS}}\left[\mathbbm{1}_{\{\tau_{y}=s\}}\right]=\frac{1}{(1+L)!} \sum_{c_{y}=0}^{1}\lambda_{s}^{1-c_{y}}\beta^{c_{y}}
Here we have to keep the product over all $x$ and the "correlated coordinate" hidden in the product $y$.
